\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-01-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
implenemet the comments from stepan

We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
starting from the beam line towards larger radius:\\
\begin{itemize}
  \item The 6~atm $^4$He target extends along the beamline forming the detector 
     central axis. It is a 6~mm diameter Kapton straw with a 27~\textmu{}m wall 
     of 292~mm length such that its entrance and exit 15~\textmu{}m aluminum windows 
     are placed outside of the detector volume. The detector and the target are 
     placed in the center of the solenoid, 64~cm upstream of the CLAS center.
   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o{}ller electrons scattered by the beam. This region is surrounded by 
      a 4 \textmu{}m thick window made of grounded aluminized Mylar.
   \item The second gas gap region extends between 20~mm and 30~mm and is 
      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
      (DME).  This region is surrounded by a 4~\textmu{}m thick window made of 
      aluminized Mylar set at $-4260$~V to serve as the cathode.
   \item The drift region is filled with the same Ne-DME gas mixture and 
      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
      The average electric field in this region is perpendicular to the beam 
      and average around 550~V/cm.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
      275~V bias is applied across each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charges 
      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
      directly on its outer side and transmit the signal to the data 
      acquisition electronics.
\end{itemize}

@@

The drift gas used in the experiment is a 80-20\% Ne-DME mixture. This choice 
has been made in order to balance the energy deposit, which is critical
for proper particle identification, with a reasonable
Lorentz angle. Calculations using the MAGBOLTZ program~\cite{Biagi:1999nwa} 
showed that with the 5~T solenoidal magnetic field, we would have a Lorentz 
angle of about 23$^\circ$ with this gas mixture.

@@

The RTPC electron collection system had 3200 readout pads. These elements were
located at the end of the amplification region, 69~mm from the central axis.
Figure \ref{fig:PADs} illustrates the configuration of the 5 by 4.45~mm pads,
where the shift between the rows was implemented to reduce aliasing. Each half 
of the RTPC had 40 rows and 40 columns of pads. The shaded region in 
Figure~\ref{fig:PADs} shows how pads were grouped to 16 channels pre-amplifier 
boards. The pre-amplifier boards, already employed in the BoNuS 
RTPC~\cite{Fenker:2008zz}, serve the dual purpose of inverting the RTPC signals 
polarity -- from negative to positive -- to match the requirements of the 
subsequent readout system, and driving the 6~m long ribbon cable that connects 
to it.

The readout system was an upgraded version of the original BoNuS RTPC system~\cite{Fenker:2008zz}, 
based ALICE-TPC front end electronic boards (FECs)~\cite{ALICE-FEE}. 
Each FEC hosted 128 channels, providing amplification and digitization of the 
input signals. For each event, 100 samples/channel were digitized by the ALTRO 
ASIC~\cite{EsteveBosch:2003bj}, operated at 10~MHz sampling frequency. In order 
to reduce the data size, the system was operated in zero-suppression mode, 
keeping data from $N_{PRE}=3$ samples before threshold crossing on the rising 
edge to $N_{POST}=3$ samples after threshold crossing on the falling edge. 
The threshold level was set on each channel just above the noise level.

@@

To verify the stability of the drift paths, this procedure was carried out 
using both the 1.204 GeV data from the beginning of the run period and the 
1.269 GeV data from the end of the run period (shown in blue on 
Figure~\ref{fig:Drift_run_number_1}). We found very similar drift paths for the 
two data sets and concluded that any changes in the system only significantly 
affected the drift speed.

\begin{figure}[t]
\centering
\includegraphics[scale=0.48]{FitResult_p2_11.pdf}
\caption{$\Delta \phi$ versus T distribution for tracks
from one bin in longitudinal position along the RTPC. The black line represents 
our firt of the drift path in this bin.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

The tracking starts with reconstructing the spacial origin of the hits using 
the extracted drift speed and drift path parameters. For each registered hit, 
we calculate a position of emission from the signal time and the pad position.  
The third step is to create chains of hits. The maximum distance between two 
close adjacent hits has to be less than 10.5 mm to chain them, which roughly 
corresponds to neighbors and next to neighbors. We fit the chains with a helix 
if they have a minimum of 10 hits. We then eliminate from the chain the hits 
that are 5 mm or farther from the fit, as they are not likely part of the same 
track. This new reduced chain is used for a second and final helix fit.

@@

\begin{figure}[tb]\centering
  \includegraphics[width=8cm]{fit_W_distribution_l.png}
  \caption{The recoil mass $W$ distribution calculated from electron kinematics 
  before (``inclusive'') and after (``exclusive'') requiring a matching track 
  in the RTPC.\label{fig:w}}
\end{figure}

>>>>

We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
starting from the beam line towards larger radius:\\
\begin{itemize}
  \item The 6~atm $^4$He target extends along the beamline forming the detector 
     central axis. It is a 6~mm diameter Kapton straw with a 27~\textmu{}m wall 
     of 292~mm length such that its entrance and exit 15~\textmu{}m aluminum windows 
     are placed outside of the detector volume. The detector and the target are 
     placed in the center of the solenoid, 64~cm upstream of the CLAS center.
   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o{}ller electrons scattered by the beam. This region is surrounded by 
      a 4 \textmu{}m thick window made of grounded aluminized Mylar.
   \item The second gas gap region extends between 20~mm and 30~mm and is 
      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
      (DME).  This region is surrounded by a 4~\textmu{}m thick window made of 
      aluminized Mylar set at $-4260$~V to serve as the cathode.
   \item The drift region is filled with the same Ne-DME gas mixture and 
      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
      The electric field in this region is perpendicular to the beam and 
      average around 550~V/cm.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
      275~V bias is applied across each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charges 
      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
      directly on its outer side and transmit the signal to the data 
      acquisition electronics.
\end{itemize}

@@

The drift gas used in the experiment is a 80\%-20\% Ne-DME mixture. This choice 
has been made in order to balance the energy deposit, which is critical
for proper particle identification, with a reasonable
Lorentz angle. Calculations using the MAGBOLTZ program~\cite{Biagi:1999nwa} 
showed that with the 5~T solenoidal magnetic field, we would have a Lorentz 
angle of about 23$^\circ$ with this gas mixture.

@@

The RTPC electron collection system had 3200 readout pads. These elements were
located at the end of the amplification region, 69~mm from the central axis.
Figure \ref{fig:PADs} illustrates the configuration of the 5 by 4.45~mm pads,
where the shift between the rows was implemented to reduce aliasing. Each half 
of the RTPC had 40 rows and 40 columns of pads. The shaded region in 
Figure~\ref{fig:PADs} shows how pads were grouped to 16 channels pre-amplifier 
boards. The pre-amplifier boards, already employed in the BoNuS 
RTPC~\cite{Fenker:2008zz}, serve the dual purpose of inverting the RTPC signals 
polarity -- from negative to positive -- to match the requirements of the 
subsequent readout system, and driving signals through the 6~m long ribbon 
cable that connects to the readout system.

The readout system was an upgraded version of the original BoNuS RTPC 
system~\cite{Fenker:2008zz}, based on ALICE-TPC front end electronic boards 
(FECs)~\cite{ALICE-FEE}.  Each FEC hosted 128 channels, providing amplification 
and digitization of the input signals. For each event, 100 samples/channel were 
digitized by the ALTRO ASIC~\cite{EsteveBosch:2003bj}, operated at 10~MHz 
sampling frequency. In order to reduce the data size, the system was operated 
in zero-suppression mode, keeping data from $N_{PRE}=3$ samples before 
threshold crossing on the rising edge to $N_{POST}=3$ samples after threshold 
crossing on the falling edge.  The threshold level was set on each channel just 
above the noise level.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.48]{FitResult_p2_11.pdf}
\caption{$\Delta \phi$ versus T distribution for tracks
from one bin in longitudinal position along the RTPC. The black line represents 
our fit of the drift path in this bin.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

@@

The tracking starts with reconstructing the spacial origin of the hits using 
the extracted drift speed and drift path parameters. For each registered hit, 
we calculate the position of emission from the signal time and the pad 
position. Then, chains of hits are created. The maximum distance between two 
close adjacent hits has to be less than 10.5 mm to chain them, which roughly 
corresponds to neighbors and next to neighbors. We fit the chains with a helix 
if they have a minimum of 10 hits. We then eliminate from the chain the hits 
that are 5 mm or farther from the fit, as they are not likely part of the same 
track. This new reduced chain is used for a second and final helix fit.

@@

\begin{figure}[tb]\centering
  \includegraphics[width=8cm]{fit_W_distribution_l.png}
  \caption{The recoil mass, $W$, distribution calculated from electron 
  kinematics before (``inclusive'') and after (``exclusive'') requiring a 
  matching track in the RTPC.\label{fig:w}}
\end{figure}
